General Game Playing and Monte-Carlo Tree Search

### 2013-11-18 doc/paper/paper.tex
added a lot to pres and fixed up paper

\begin{lstlisting}[frame=single, caption=The Legal relation translated into core.logic]
(defn legal [role action]
 (conde
  [(fresh [?w ?m?n]
    (== role ?w)
    (== action [:mark ?m ?n])
    (true [:cell ?m ?n :b])
    (true [:control ?w]))]
  [(== role :X)
   (== action :noop)
   (true [:control :O])]
  [(== role :O)
   (== action :noop)
   (true [:control :X])]))
\end{lstlisting}

@@

 In order to accomplish these tasks, each relation takes an addition argument of the environment. Whenever the relation would make a call to another relation, it instead first fetches the relation from the environment and then calls it. This results in the Legal relation shown above now looking like so:

\begin{lstlisting}[frame=single, caption=The Legal relation translated into core.logic]
(defn legal [env role action]
 (conde
  [(fresh [?w ?m?n]
    (== role ?w)
    (== action [:mark ?m ?n])
    ((env :true) [:cell ?m ?n :b])
    ((env :true) [:control ?w]))]
  [(== role :X)
   (== action :noop)
   ((env :true) [:control :O])]
  [(== role :O)
   (== action :noop)
   ((env :true) [:control :X])]))
\end{lstlisting}

@@

After this pre-processing is finished, creating the core.logic relations is as simple as creating code (as Clojure data structures) that represents the relations as a function and then calling \texttt{eval} on that code. The code is created according to the rules exemplified below.
\begin{lstlisting}[frame=single, caption=Reflexive head calls turn into unifications]
;; Transforming Legal
(legal ?w (mark ?x ?y))
;; -~->
(== role ?w)
(== move [:mark ?x ?y]
\end{lstlisting}

\begin{lstlisting}[frame=single,caption=All other relations reference the environment]
(true (cell 1 1 b))
;; -~->
((env :true) [:cell 1 1 :b])
\end{lstlisting}

\begin{lstlisting}[frame=single,caption=not turns into negation as failure constraint (nafc)]
(not (line X))
;; -~->
(nafc (env :line) X)
\end{lstlisting}

>>>>

\begin{lstlisting}[frame=single, caption=The Legal relation translated into core.logic]
(defn legal [role action]
 (conde
  [(fresh [?w ?m ?n]
    (== role ?w)
    (== action [:mark ?m ?n])
    (true [:cell ?m ?n :b])
    (true [:control ?w]))]
  [(== role :X)
   (== action :noop)
   (true [:control :O])]
  [(== role :O)
   (== action :noop)
   (true [:control :X])]))
\end{lstlisting}

@@

 In order to accomplish these tasks, each relation takes an additional argument of the environment. Whenever the relation would make a call to another relation, it instead first fetches the relation from the environment and then calls it. This results in the Legal relation shown above now looking like so:

\begin{lstlisting}[frame=single, caption=The Legal relation translated into core.logic]
(defn legal [env role action]
 (conde
  [(fresh [?w ?m ?n]
    (== role ?w)
    (== action [:mark ?m ?n])
    ((env :true) env [:cell ?m ?n :b])
    ((env :true) env [:control ?w]))]
  [(== role :X)
   (== action :noop)
   ((env :true) env [:control :O])]
  [(== role :O)
   (== action :noop)
   ((env :true) env [:control :X])]))
\end{lstlisting}

@@

After this pre-processing is finished, creating the core.logic relations is as simple as creating code (as Clojure data structures) that represents the relations as a function and then calling \texttt{eval} on that code. The code is created according to the rules exemplified below.
\begin{lstlisting}[frame=single, caption=Reflexive head calls turn into unifications]
;; Transforming Legal
(legal ?w (mark ?x ?y))
;; -~->
(== role ?w)
(== move [:mark ?x ?y])
\end{lstlisting}

\begin{lstlisting}[frame=single,caption=All other relations reference the environment]
(true (cell 1 1 b))
;; -~->
((env :true) env [:cell 1 1 :b])
\end{lstlisting}

\begin{lstlisting}[frame=single,caption=not turns into negation as failure constraint (nafc)]
(not (line X))
;; -~->
(nafc (env :line) env :X)
\end{lstlisting}
